After high-school, I try mathematics at university. While the subject was and still is of great interest to me, the amount of work and the rhythm was too fast for me. 
To stay in the scientific/technical world but with more hands-on practice, I made an accelerated apprenticeship in computer science and became an IT guy. 
I then moved to a university of applied sciences where I continued to study computer science and got a bachelor in software engineering while working in parallel in a small sport import company providing them with helpdesk support.

In 2005, at the end of my studies, I moved to Finland where I started to work as a research engineer in Metropolia University of Applied Sciences (called Evtek at that time). 
Very quickly, I received the opportunity to teach software related topics such as web technologies, programming languages, software engineering and data management in parallel to my research tasks. 
After completing my master degree in mobile programming last year and with the hope of getting a lecturer position, vocational studies became a must.

For ten years now, I have been working for many EU projects with many related to pedagogy. 
In 2005, I started by maintaining the NetPro application and server which was a online learning environment, similar to e.g. moodle, where teacher could upload teaching material, create assignment for students, assess them and grade the students,\ldots
From 2005 to 2011, I participated in the KP-Lab\footnote{Knowledge Practices Laboratory (\url{http://www.kp-lab.org/})} where Paavola and Hakkarainen \cite{Paavola_2005} developed the Trialogical Learning metaphor\footnote{see also \url{http://kplab.evtek.fi:8080/wiki/Wiki.jsp?page=TrialogicalLearning}}. In this project we created a web application to support the collaborative learning around shared objects.
This platform was continued in the COOP-PBL\footnote{\url{http://coop-pbl.com/}} project.
From 2012 to 2014, I was part of the Creating Knowledge through Design & Conceptual Innovation project\footnote{\url{http://www.knowledge-through-design.uni-kiel.de/}} where we built the \url{http://t-h-inker.net/} community-oriented innovation platform for exchange and cooperative work of interested people from all disciplines (teachers, researchers, students, creative knowledge workers) to topics like design thinking and divergent thinking, knowledge creation and inquiry. 

Currently, I am part of the Knork\footnote{Promoting Knowledge Work Practices in Education (\url{http://knork.info})} project where we develop and test pedagogical methods, digital tools and teacher training models to improve competencies and practices in secondary and higher education. In parallel, I am participating in the Creative Classroom\footnote{\url{http://www.bcskoolitus.ee/creativeclass/?page_id=79}} project where we are training Estonian teachers  to enable innovative tools and methods to be used in delivering the national curricula.






  
  
  
  
  
  